---
title: "getting-started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{getting-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `DART2` package accompanies the paper "DART2: a robust multiple testing method to smartly leverage helpful or misleading ancillary information". It is a new multiple-testing method to leverage ancillary information for improving testing performance, regardless of whether the ancillary information is helpful or misleading.

This document provides a simple example about how to use the functions in DART2 package. Please refer to the paper for the in-depth information (e.g. data preprocess, hypotheses set up, tuning parameter selection, etc.) about the data analysis. 

```{r setup}
library(DART2)
```



Here, we show how to apply `DART2` based on the existing aggregation tree.
\par
The sample data we used contains 1000 hypothesis, each hypothesis links to a test statistics that suppose to follow standard normal distibution under null (`Sample_list$stat`). The 5-layer aggregation tree (`Sample_list$ATree`) is presented in the form of list, and `Sample_list$Atree[[X]]` stands for the node combination on layer $X+1$.

Each `Sample_list$Atree[[X]]` is structured as a matrix, with columns representing nodes at layer $X$
X and rows representing nodes at layer $X+1$
after combination. In this matrix, a value of $1$ indicates that the corresponding node at layer 
$X$ is included in the combination forming the node at layer $X+1$, while a $0$ indicates it is not.

For example, consider a $2\times 4$ matrix 
\begin{bmatrix}
1 & 1 & 0 & 0\\
0 & 0 & 1 & 1
\end{bmatrix}
Then this matrix means the layer $X$ contains $4$ nodes and the outcoming layer $X+1$ has $2$ nodes. the first node on layer $X+1$ is formed by combining the first two nodes on layer $X$, and the second node on layer $X+1$ is formed by combining the 3rd and 4th nodes on layer $X$.




```{r}
#Sample_list is a build-in data in DART2 package. It is a list contains 2 elements: 1)ATree: aggregation tree, 2)stat: contains the test statistics

# run DART2_list
test_result <- DART2_list(Llist=Sample_list$ATree,T1=Sample_list$stat)

head(test_result)
```


Given in a lot of applications, the hypothesis is simply orderes, DART2 package also introduces the function DART2_order for situations where hypotheses are pre-ordered. Unlike other functions, DART2_order does not require the input of an aggregation tree. Instead, it automatically constructs the aggregation tree based on the provided order of hypotheses, streamlining the process.

The sample data we used also contains 1000 hypothesis. The data is presented in the form of data frame. The data frame contains 4 variables 1) "hypo": index of hypothesis; 2) "pval": p-values for each hypothesis; 3)"z": test statistics for each hypothesis; 4) "orderp": the order of hypothesis based on external information.

```{r}
#Sample_order is a build-in data.frame in DART2 package.

# run DART2_order
test_result <- DART2_order(Sample_order)

head(test_result)
```


